Self Regulation Ontology Retest Analyses

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

>>>>

```{r}
rel_comp %>% 
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean ICC")+
  ylim(-0.4,1)

ggsave('LitTaskVsSurvey.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```
